Output Summary

### 2023-05-04 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Consistency updates: 13-post-vs-prior.Rmd

```{r post-v-prior-fig-sizes}
# set global knitting options
knitr::opts_chunk$set(fig.width = 6, fig.height = 5)
```

@@

  # if some portion of one of the dists is not shown, include a message
  if (p_post_keep < 1 | p_prior_keep < 1) {
    nice_round = function(x, digits = 2) {
      x_round = round(x, digits = digits)
      if (x_round == 0 & x > 0) x_out  = "<0.01" else x_out = x_round
      x_out
    }

    legend(x = usr[1] - xdiff * 0, y = usr[4] + ydiff * 0.025, xpd = TRUE,
           legend = c(nice_round(1 - p_prior_keep), nice_round(1 - p_post_keep)),
           text.col = c(prior_col, post_col), bty = "n", title.col = "black",
           title = "P Not Shown", cex = 0.8
    )
  }
}
```

@@

```{r mu_phi_O1_O2-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O1_O2[origin,pop]", prior_param = "mu_phi_O1_O2_pr",
                  origin = o_nor, xlim = c(0,1), legend_loc = "topleft"
)
```

@@

```{r mu_phi_O2_O3-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O2_O3[origin,pop]", prior_param = "mu_phi_O2_O3_pr",
                  origin = o_nor, xlim = c(0,1), legend_loc = "topleft"
)
```

@@

```{r}
# set these figure options for all plots in this section
y_max = 0.15
xlim = c(-1,1)
knitr::opts_chunk$set(fig.width = 5, fig.height = 6)
```

>>>>

```{r post-v-prior-fig-sizes}
# set global knitting options
knitr::opts_chunk$set(fig.width = p4_width, fig.height = p4_height)
```

@@

  # if some portion of one of the dists is not shown, include a message
  # if (p_post_keep < 1 | p_prior_keep < 1) {
  #   nice_round = function(x, digits = 2) {
  #     x_round = round(x, digits = digits)
  #     if (x_round == 0 & x > 0) x_out  = "<0.01" else x_out = x_round
  #     x_out
  #   }
  #   
  #   legend(x = usr[1] - xdiff * 0, y = usr[4] + ydiff * 0.025, xpd = TRUE,
  #          legend = c(nice_round(1 - p_prior_keep), nice_round(1 - p_post_keep)),
  #          text.col = c(prior_col, post_col), bty = "n", title.col = "black",
  #          title = "P Not Shown", cex = 0.8
  #   )
  # }
}
```

@@

```{r mu_phi_O1_O2-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O1_O2[origin,pop]", prior_param = "mu_phi_O1_O2_pr",
                  origin = o_nor, xlim = c(0,1), legend_loc = "topright"
)
```

@@

```{r mu_phi_O2_O3-post-v-prior}
post_v_prior_pops(post_param = "mu_phi_O2_O3[origin,pop]", prior_param = "mu_phi_O2_O3_pr",
                  origin = o_nor, xlim = c(0,1), legend_loc = "topright"
)
```

@@

```{r}
# set these figure options for all plots in this section
y_max = 0.15
xlim = c(-1,1)
knitr::opts_chunk$set(fig.width = p4_height, fig.height = p4_width, out.width = "50%")
```
